---
title: "TogglAnalysis"
author: "Avery Chan"
date: "5/30/2021"
output:
  html_document:
    # toc: yes
    # toc_float: true
    # number_sections: true
    # theme: united
    df_print: paged
    code_folding: show
---

## Setup

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(lubridate)
```

### Import the data

```{r import data}
data2020 <- read_csv("Toggl_time_entries_2020-01-01_to_2020-12-31.csv")
data2021 <- read_csv("Toggl_time_entries_2021-01-01_to_2021-12-31.csv")

# glimpse(data2020)
```

### Clean Data

```{r clean data}
data2020 <- data2020 %>%
  select(Project,
         Description,
         `Start date`,
         `Start time`,
         `End date`,
         `End time`,
         Duration,
         Tags)
data2021 <- data2021 %>%
  select(Project,
         Description,
         `Start date`,
         `Start time`,
         `End date`,
         `End time`,
         Duration,
         Tags)
glimpse(data2020)
```

```{r}
data2020 %>% 
  group_by(Project) %>% 
  summarise(
    n = n(),
    hms = sum(Duration) %>% hms::as_hms(),
    sec = sum(Duration)
  )

timeWorkHMS <- data2020 %>% 
  pull(Duration) %>% 
  sum() %>% 
  hms::as_hms()

timeWork <- data2020 %>% 
  pull(Duration) %>% 
  sum()

# fraction of entire time spent working
timeWork / dyears(1)

# estimated sleep fraction if I sleep 7 hours each night
365 * dhours(7) / dyears(1)

# 8 hours
365 * dhours(8) / dyears(1)

# data2020 %>% 
#   slice_min(`Start date`)
# 
# data2020 %>% 
#   slice_max(`Start date`)
```
## Analysis

### Basic Grouping

Basic grouping by category

```{r}

```


### Heatmap

Heat map of when during the day I worked
Heat map of sorts of type of work I did when
Possible heatmap of what times I work at (and what type when)

### Scheuldes

See if you can distinguish schedules that were established at any point in time. Bonus points if I do this numerically with differences or something.

Productivty over time vs what I was doing (ie time spent working during semester and summer and weekend and weekday)

It's interesting I independently (two times) came up with the same questions - I am interested in seeing this.












